Semi-Supervised Factored Logistic Regression for High-Dimensional Neuroimaging Data

### 2015-06-04 paper_nips/paper.tex
abstract

\begin{abstract}
Imaging neuroscience links human behavior to aspects of brain
biology in ever-increasing datasets.
%
Existing neuroimaging methods typically perform either discovery of unknown
neural structure or testing of neural structure associated with mental tasks.
%
However, testing hypotheses on the neural correlates of
larger mental task sets
necessitates adequate representation of the observations.
%
We therefore propose to optimize
representation modelling and task classification in
a unified statistical learning problem.
%
A multinomial logistic regression is introduced that is
constrained by factored coefficients with a representation-enforcing
autoencoder.
%
We show that this approach yields more accurate and interpretable
neural models of psychological tasks in a reference dataset,
as well as better generalization to other datasets.
%

>>>>

\begin{abstract}
Imaging neuroscience links human behavior to aspects of brain
biology in ever-increasing datasets.
%
Existing neuroimaging methods typically perform either discovery of unknown
neural structure or testing of neural structure associated with mental tasks.
%
However, testing hypotheses on the neural correlates of
larger mental task sets
necessitates adequate representations of the observations.
%
We therefore propose to blend
representation modelling and task classification into
a unified statistical learning problem.
%
A multinomial logistic regression is introduced that is
constrained by factored coefficients and coupled with an autoencoder.
%
We show that this approach yields more accurate and interpretable
neural models of psychological tasks in a reference dataset,
as well as better generalization to other datasets.
%
